Plant-pollintor networks worldwide are composed by the same specific building

### 2021-06-16 Draft/Draft.Rmd
Edits on functional groups pie charts

The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale). Research of the network structure have proven common invariant structural properties across them including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or the higher number of pollinator species than plant species [@bluthgen2007]. In addition, species phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of pairwise plant-pollinator interactions [@bartomeus2016; @stang2006; @peralta2020]. However, both species level information or an holistic view of the full network involves missing relevant information for the understanding of ecological processes [@simmons2019].

>>>>

The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale). Research of the plant-pollinator network structure have proven common invariant structural properties across them including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or the higher number of pollinator species than plant species [@bluthgen2007]. In addition, species phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of pairwise plant-pollinator interactions [@bartomeus2016; @stang2006; @peralta2020]. However, both species level information or an holistic view of the full network involves missing relevant information for the understanding of ecological processes [@simmons2019].
